General constraints on magic distillation protocols from statistical mechanics

### 2021-06-06 magic_paper.tex
Additional appendix edits.

4. This follows immediately from Schur-convexity of $D_\alpha$.
\end{proof}
\nick{Combining ALL the properties above (and nothing more) leads to the general bound}

@@

\begin{proof} If we have $H_\alpha (W_\rho(\x)) <0 $ then this implies that $\log \sum_{\x} W_\rho (\x)^\alpha > 1$, however it is known that $H_\alpha$ is always non-negative on probability distributions and therefore $W_\rho(\x)$ must be a strict quasi-distribution with negativity.

Conversely, suppose $\rho$ has negativity in its Wigner representation. This implies that $\sum_{\x} |W_\rho (\x)| >1$. We now consider $\sum_{\x} W_\rho (\x)^{a/b}$ for $a/b >1$ and $a$ even and $b$ odd. We have that
\begin{align}
\sum_{\x} W_\rho (\x)^{a/b} &= \sum_{\x} |W_\rho (\x)|^{a/b} \nonumber \\
&= \sum_{\x} |W_\rho (\x)|^{1+ \epsilon},
\end{align}
where $\epsilon = a/b - 1 >0$. By choosing $a$ and $b$ appropriately we can make $\epsilon$ arbitrarily close to $0$ and therefore there exists a sequence $\epsilon_n=a_n/b_n$ such that
\begin{equation}
\sum_{\x} |W_\rho (\x)|^{1+ \epsilon_n} \rightarrow \sum_{\x} |W_\rho (\x)| >1.
\end{equation}
\nick{In this step, we also need to show that $H_\alpha$ is increasing in $\alpha$}
Therefore, $H_\alpha (W_\rho (\x)) <0 $ at some point in the sequence, which completes the proof.
\end{proof}

>>>>

4. This follows immediately from Schur-convexity of $D_\alpha$.
\end{proof}

@@

\begin{proof} If we have $H_\alpha (W_\rho(\x)) <0 $ for $\alpha >1$ then this implies that $\log \sum_{\x} W_\rho (\x)^\alpha > 1$, however it is known that $H_\alpha$ is always non-negative on probability distributions and therefore $W_\rho(\x)$ must be a strict quasi-distribution with negativity.

Conversely, suppose $\rho$ has negativity in its Wigner representation. This implies that $\sum_{\x} |W_\rho (\x)| >1$. We now consider $\sum_{\x} W_\rho (\x)^{a/b}$ for $a/b >1$ and $a$ even and $b$ odd. We have that
\begin{align}
\sum_{\x} W_\rho (\x)^{a/b} &= \sum_{\x} |W_\rho (\x)|^{a/b} \nonumber \\
&= \sum_{\x} |W_\rho (\x)|^{1+ \epsilon},
\end{align}
where $\epsilon = a/b - 1 >0$. By choosing $a$ and $b$ appropriately we can make $\epsilon$ arbitrarily close to $0$. More precisely, there exists a sequence $\epsilon_n=a_n/b_n$ with valid integer pairs $a_n, b_n$ such that
\begin{equation}
\sum_{\x} |W_\rho (\x)|^{1+ \epsilon_n} \rightarrow \sum_{\x} |W_\rho (\x)| >1.
\end{equation}
Since $\frac{1}{1-\alpha}= -\frac{b_n}{a_n} <0$ for any $n$ it follows that $H_\alpha (W_\rho (\x)) = \frac{1}{1-\alpha} \log \sum_{\x} W_\rho (\x)^\alpha  <0 $ at some point in the sequence, which completes the proof.
\end{proof}
